---
title: "Precised computation of the probabilities"
output: html_notebook
---



\newcommand{\Ecal}{\mathcal{Y}}
\newcommand{\Esp}[1]{\mathbb{E}\left[#1\right]}
\newcommand{\Espf}[1]{\mathbb{E}_{f_{X}}\left[#1\right]}
\newcommand{\Espbiais}[1]{\mathbb{E}_{\biais}\left[#1\right]}
\newcommand{\centro}{\gamma}
\newcommand{\Gamm}{\Gamma}
\newcommand{\norm}[1]{\lVert #1 \lVert_{\Ecal}}
\newcommand{\rep}{q_{\Gamm}}
\newcommand{\qgs}{q_{{\Gamm}^{\star}}}
\newcommand{\qgk}{q_{{\Gamm}^{[k]}}}
\newcommand{\scalprodE}[2]{\langle #1,#2\rangle_{\Ecal}}
\newcommand{\scalprod}[2]{\Esp{\scalprodE{#1}{#2}}}
\newcommand{\scalprodomega}[2]{\Esp{\scalprodE{#1}{#2}}}
\newcommand{\biais}{\nu}
\newcommand{\repo}{q^{0}_{\Gamm}}
\newcommand{\Xtildek}{\tilde{X}^{k}}
\newcommand{\Espprod}[1]{\mathbb{E}_{\Omega_{1}, \Omega_{2}}\left[#1\right]}
\newcommand{\var}{\mathbb{V}}
\newcommand{\clust}[2]{C^{#1}_{#2}}
\newcommand{\yinclust}[3]{#1 \in \clust{#2}{#3}}
\newcommand{\card}{\ell}
\newcommand{\campbell}{h}
\newcommand{\aff}{a}
\newcommand{\Jcal}{\mathcal{J}}
\newcommand{\Ytrue}{{Y}}
\newcommand{\Ypred}{\hat{Y}}
\newcommand{\Ysimu}{Y_{simu}}
\newcommand{\camprandom}{H}
\newcommand{\dime}{64}
\newcommand{\Gammaref}{\Gamma^{\star}}
\newcommand{\Gammapred}{\hat\Gamma_{\star}}
\newcommand{\Gammasimu}{\Gamma_{simu}}
\newcommand{\erreurproba}{\varepsilon}
\newcommand{\erreurprobarelative}{\delta}
\newcommand{\erreurprobarelativecoastal}{\erreurprobarelative}

\newcommand{\nbgamma}{100}
\newcommand{\nbpilot}{v}
\newcommand{\ntrue}{n_{t}}
\newcommand{\npred}{n_{pred}}
\newcommand{\nsimu}{n_{\mathrm{simu}}}
\newcommand{\Dspace}{\chi}
\newcommand{\supp}{{\mathrm{supp}}}
\newcommand{\thresh}{t}
\newcommand{\estim}{\hat{E}}
\newcommand{\nbsim}{m_{\mathrm{simu}}}
\newcommand{\ntrain}{n_{\mathrm{train}}}
\newcommand{\ntest}{n_{\mathrm{test}}}
\newcommand{\eqdef}{:=}
\newcommand{\Ypca}{Y^{\mathrm{pca}}}
\newcommand{\Yproj}{Y_{\mathrm{proj}}}
\DeclareMathOperator*{\argmax}{arg\,max}
\DeclareMathOperator*{\argmin}{arg\,min}
\newcommand\dsone{\mathds{1}}
\newcommand{\Ecal}{\mathcal{E}}
\newcommand{\Esp}[1]{\mathbb{E}\left[#1\right]}
\newcommand{\centro}{\gamma}
\newcommand{\Gamm}{\Gamma}
\newcommand{\norm}[1]{\lVert #1 \lVert_{\mathcal{E}}}
\newcommand{\rep}{q_{\Gamm}}
\newcommand{\qgs}{q_{{\Gamm}^{\star}}}
\newcommand{\qgk}{q_{{\Gamm}^{[k]}}}
\newcommand{\scalprodE}[2]{\langle #1,#2\rangle_{\mathcal{E}}}
\newcommand{\scalprod}[2]{\Esp{\scalprodE{#1}{#2}}}
\newcommand{\repo}{q^{0}_{\Gamm}}
\newcommand{\Xtildek}{\tilde{X}^{k}}

The idea here is to compute the probabilities associated to the optimal quantization $\Gamm^{\star}$ obtained in the notebook lloyd_true.Rmd, with a very large sample $(\tilde{X}^{(k)})_{k \in \{1,\dots,10^7\}}$ i.i.d of density function $\biais$.


```{r}
load("NewFitting_Charlie_v090821.RData")

source.all("GpOutput2D-main/GpOutput2D/R")
source("Campbell2D.R")
source("Campbell_utils.R")
```

We get the optimal quantization 

```{r}
load("lloyd_res_true.RData")
gamma_star = lloyd_res_true$gamma
```

```{r}
dim_map = c(64,64)

z1 = seq(-90,90,l=dim_map[1])
z2 = seq(-90,90,l=dim_map[2])

```

We sample $(\tilde{X}^{(k)})_{k \in \{1,\dots,10^7\}}$ i.i.d of density function $\biais$

```{r}
set.seed(1234)
n=10^7
Xtilde = matrix(runif(n =5*n), ncol = 5)
Xtilde = cbind(Xtilde, sample(1:10,size = n, replace = TRUE) / 10)

unif = runif(n) 
Xtilde = cbind(Xtilde, (unif <= 8/13)*runif(n))

Xtilde = cbind(Xtilde, rep(-1,n))
Xtilde = transform_X(Xtilde)



```

We compute the weights $\left(\frac{f_{X}(\tilde{X}^{(k)})}{\biais(\tilde{X}^{(k)})}\right){_{k \in \{1,\dots,10^7\}}}$, stored in the vector densite_vec

```{r}
Xtilde_phy = ((Xtilde + 1)/6)[,1:7]
for(i in 1:5){
  Xtilde_phy[,i] = Xtilde_phy[,i] * (df_bornes[i,2]-df_bornes[i,1]) + df_bornes[i,1]
}
Xtilde_phy[,6] = Xtilde_phy[,6]*10
```

```{r,  results='hide'}
registerDoParallel(cores = 10)

densite_vec = list()
st = Sys.time()
for(batch in 1:100){
  print(batch)
  densite_vec[[batch]] = foreach (it = 1:10^5, .combine = 'c') %dopar% {densite_ratio_full(as.numeric(Xtilde_phy[((batch-1)*10^5+1):(batch*10^5),][it,]))}
  
}




```
We compute the Voronoi cell associated to every $Y(\tilde{X}^{k})$

```{r, results='hide'}
numeros = c()
for(it in 1:100){
  print(it)
  maps_true = Campbell2D(Xtilde[((it-1)*10^5+1):(it*10^5),], z1, z2)
  numeros = c(numeros, get_numeros(maps_true,gamma_star))


}
rm(maps_true)

```

And for each voronoi cell, we compute $\hat{P}^{\mathrm{true}}_{\ntrue}(\Gamm^{\star},j) = \frac{1}{\ntrue} \sum^{\ntrue}_{k=1} \mathbb{1}_{\yinclust{\Ytrue(\tilde{X}^{(k)})}{\Gamm^{\star}}{j} }\frac{f_{X}(\tilde{X}^{(k)})}{\biais(\tilde{X}_{k})}$ 

```{r}
get_probas(numeros, unlist(densite_vec))
```

