---
title: "Accurate computation of the probabilities"
output: html_notebook
---

\newcommand{\Gamm}{\Gamma}
\newcommand{\biais}{\nu}
\newcommand{\yinclust}[3]{#1 \in \clust{#2}{#3}}
\newcommand{\Ytrue}{{Y}}
\newcommand{\clust}[2]{C^{#1}_{#2}}

The idea here is to compute the probabilities associated to the optimal quantization $\Gamm^{\star}$ obtained in the notebook PMalgo_true.Rmd, with a very large sample $(\tilde{x}^k)_{k \in \{1,\dots,10^7\}}$ i.i.d of density function $\biais$.


```{r}
source.all("GpOutput2D-main")
source.all("FunQuant-0.1.3/R")
source("Campbell2D.R")
source("Campbell_utils.R")
```

We get the optimal quantization 

```{r}
load("lloyd_res_true.RData")
gamma_star = lloyd_res_true$gamma
```

```{r}
dim_map = c(64,64)

z1 = seq(-90,90,l=dim_map[1])
z2 = seq(-90,90,l=dim_map[2])

```

We sample $(\tilde{x}^k)_{k \in \{1,\dots,10^7\}}$ i.i.d of density function $\biais$

```{r}
set.seed(1234)
n=10^7
Xtilde = matrix(runif(n =5*n), ncol = 5)
Xtilde = cbind(Xtilde, sample(1:10,size = n, replace = TRUE) / 10)

unif = runif(n) 
Xtilde = cbind(Xtilde, (unif <= 8/13)*runif(n))

Xtilde = cbind(Xtilde, rep(-1,n))
Xtilde = transform_X(Xtilde)



```

We compute the weights $\left(\frac{f_{X}(\tilde{x}^k)}{\biais(\tilde{x}^k)}\right){_{k \in \{1,\dots,10^7\}}}$, stored in the vector densite_vec

```{r}
Xtilde_phy = ((Xtilde + 1)/6)[,1:7]
for(i in 1:5){
  Xtilde_phy[,i] = Xtilde_phy[,i] * (df_bornes[i,2]-df_bornes[i,1]) + df_bornes[i,1]
}
Xtilde_phy[,6] = Xtilde_phy[,6]*10
```

```{r,  results='hide'}
registerDoParallel(cores = 24)

density_ratio = list()
st = Sys.time()
for(batch in 1:100){
  if(batch%%10==0){print(batch)}
  density_ratio[[batch]] = compute_density_ratio(fX,g, Xtilde_phy[((batch-1)*10^5+1):(batch*10^5),])
}





```
## With the true maps

We compute the Voronoi cell associated to every $Y(\tilde{x}^{k})$

```{r, results='hide'}
cell_numbers = c()
for(it in 1:100){
  print(it)
  maps_true = Campbell2D(Xtilde[((it-1)*10^5+1):(it*10^5),], z1, z2)
  cell_numbers = c(cell_numbers, get_cell_numbers(maps_true,gamma_star))


}
rm(maps_true)

```

And for each voronoi cell, we compute a realization of $\hat{P}_{\tilde{n}}(\Gamm^{\star},j, \Ytrue) = \frac{1}{\tilde{n}} \sum^{\tilde{n}}_{k=1} \mathbb{1}_{\yinclust{\Ytrue(\tilde{X}^k)}{\Gamm^{\star}}{j} }\frac{f_{X}(\tilde{X}^k)}{\biais(\tilde{X}^{k})}$ with $\tilde{n} = 10^7$

Here are the probabilities obtained with the true maps

```{r}
probas_true = get_probas(density_ratio = unlist(density_ratio), cell_numbers = cell_numbers, cells = 1:5)
probas_true
```

## With the predicted maps

```{r}
X_training = Xtilde[1:1300,]
Y_training = Campbell2D(X_training,z1,z2)

set.seed(1)

metamodel = fit_metamodel(design_train = data.frame(x = X_training)[,1:7], outputs_train = Y_training, seed = 1, ncoeff = 2000, npc = 6,control = list(trace = 0))



```

```{r}

batch_size = 10^4 #we will compute the voronoi cell by batch of 10^4 maps

numeros_pred = c()
for(batch in 1:(nrow(Xtilde)%/%batch_size)){ #for each batch
  if(batch %% 50 == 0){print(batch)}
  Xtilde_batch = Xtilde[((batch-1)*batch_size+1):(batch*batch_size),] #we get the inputs of the batch
  map_metamodel = foreach(i = 1:100, .combine = "c") %dopar% {predict_outputs(metamodel_fitted = metamodel, design_test = data.frame(Xtilde_batch[((i-1)*100+1):(i*100),1:7]), type = "UK", compute = FALSE)} #we predict the maps associated to these inputs
  map_metamodel = array(map_metamodel, dim = c(64,64,10000)) 
  numeros_pred = c(numeros_pred, get_cell_numbers(outputs = map_metamodel,gamma = gamma_star)) #computed the associated voronoi cells number

}

numeros_pred[1:1300] = cell_numbers[1:1300] #the training voronoi cell number are affected to the training maps
```

Here are the probabilities obtained with the predicted maps

```{r}
probas_pred = get_probas(density_ratio = unlist(density_ratio), cell_numbers = numeros_pred, cells = 1:5)
print(probas_pred)
print(probas_true)
```

