---
title: "Accurate computation of the probabilities"
output: html_notebook
---

\newcommand{\Ecal}{\mathcal{Y}}
\newcommand{\Esp}[1]{\mathbb{E}\left[#1\right]}
\newcommand{\Espf}[1]{\mathbb{E}_{f_{X}}\left[#1\right]}
\newcommand{\Espbiais}[1]{\mathbb{E}_{\biais}\left[#1\right]}
\newcommand{\centro}{\gamma}
\newcommand{\Gamm}{\Gamma}
\newcommand{\norm}[1]{\lVert #1 \lVert_{\Ecal}}
\newcommand{\rep}{q_{\Gamm}}
\newcommand{\qgs}{q_{{\Gamm}^{\star}}}
\newcommand{\qgk}{q_{{\Gamm}^{[k]}}}
\newcommand{\scalprodE}[2]{\langle #1,#2\rangle_{\Ecal}}
\newcommand{\scalprod}[2]{\Esp{\scalprodE{#1}{#2}}}
\newcommand{\scalprodomega}[2]{\Esp{\scalprodE{#1}{#2}}}
\newcommand{\biais}{\nu}
\newcommand{\repo}{q^{0}_{\Gamm}}
\newcommand{\Xtildek}{\tilde{X}^{k}}
\newcommand{\Espprod}[1]{\mathbb{E}_{\Omega_{1}, \Omega_{2}}\left[#1\right]}
\newcommand{\var}{\mathbb{V}}
\newcommand{\clust}[2]{C^{#1}_{#2}}
\newcommand{\yinclust}[3]{#1 \in \clust{#2}{#3}}
\newcommand{\card}{\ell}
\newcommand{\campbell}{h}
\newcommand{\aff}{a}
\newcommand{\Jcal}{\mathcal{J}}
\newcommand{\Ytrue}{{Y}}
\newcommand{\Ypred}{\hat{Y}}
\newcommand{\Ysimu}{Y_{simu}}
\newcommand{\camprandom}{H}
\newcommand{\dime}{64}
\newcommand{\Gammaref}{\Gamma^{\star}}
\newcommand{\Gammapred}{\hat\Gamma^{\star}}
\newcommand{\Gammasimu}{\Gamma_{simu}}
\newcommand{\erreurproba}{\varepsilon}
\newcommand{\erreurprobarelative}{\epsilon_P^{MM}}
\newcommand{\erreurprobarelativecoastal}{\erreurprobarelative}
\newcommand{\nbgamma}{100}
\newcommand{\nbpilot}{v}
\newcommand{\ntrue}{n_{\mathrm{maps}}}
\newcommand{\npred}{n_{\mathrm{maps}}}
\newcommand{\nsimu}{n_{\mathrm{simu}}}
\newcommand{\Dspace}{\chi}
\newcommand{\supp}{{\mathrm{supp}}}
\newcommand{\thresh}{t}
\newcommand{\estim}{\hat{E}}
\newcommand{\nbsim}{m_{\mathrm{simu}}}
\newcommand{\ntrain}{n_{\mathrm{train}}}
\newcommand{\ntest}{n_{\mathrm{test}}}
\newcommand{\eqdef}{:=}
\newcommand{\Ypca}{Y^{\mathrm{pca}}}
\newcommand{\Yproj}{Y_{\mathrm{proj}}}
\newcommand{\nvar}{n_{v}}
\newcommand{\nerr}{n_{e}}

The idea here is to compute the probabilities associated to the optimal quantization $\Gamm^{\star}$ obtained in the notebook PMalgo_true.Rmd, with a very large sample $(\tilde{X}^{(k)})_{k \in \{1,\dots,10^7\}}$ i.i.d of density function $\biais$.


```{r}
load("NewFitting_Charlie_v090821.RData")

source.all("GpOutput2D-main/GpOutput2D/R")
source("Campbell2D.R")
source("Campbell_utils.R")
```

We get the optimal quantization 

```{r}
load("lloyd_res_true.RData")
gamma_star = lloyd_res_true$gamma
```

```{r}
dim_map = c(64,64)

z1 = seq(-90,90,l=dim_map[1])
z2 = seq(-90,90,l=dim_map[2])

```

We sample $(\tilde{X}^{(k)})_{k \in \{1,\dots,10^7\}}$ i.i.d of density function $\biais$

```{r}
set.seed(1234)
n=10^7
Xtilde = matrix(runif(n =5*n), ncol = 5)
Xtilde = cbind(Xtilde, sample(1:10,size = n, replace = TRUE) / 10)

unif = runif(n) 
Xtilde = cbind(Xtilde, (unif <= 8/13)*runif(n))

Xtilde = cbind(Xtilde, rep(-1,n))
Xtilde = transform_X(Xtilde)



```

We compute the weights $\left(\frac{f_{X}(\tilde{X}^{(k)})}{\biais(\tilde{X}^{(k)})}\right){_{k \in \{1,\dots,10^7\}}}$, stored in the vector densite_vec

```{r}
Xtilde_phy = ((Xtilde + 1)/6)[,1:7]
for(i in 1:5){
  Xtilde_phy[,i] = Xtilde_phy[,i] * (df_bornes[i,2]-df_bornes[i,1]) + df_bornes[i,1]
}
Xtilde_phy[,6] = Xtilde_phy[,6]*10
```

```{r,  results='hide'}
registerDoParallel(cores = 10)

densite_vec = list()
st = Sys.time()
for(batch in 1:100){
  print(batch)
  densite_vec[[batch]] = foreach (it = 1:10^5, .combine = 'c') %dopar% {densite_ratio_full(as.numeric(Xtilde_phy[((batch-1)*10^5+1):(batch*10^5),][it,]))}
  
}




```
## With the true maps

We compute the Voronoi cell associated to every $Y(\tilde{X}^{k})$

```{r, results='hide'}
numeros = c()
for(it in 1:100){
  print(it)
  maps_true = Campbell2D(Xtilde[((it-1)*10^5+1):(it*10^5),], z1, z2)
  numeros = c(numeros, get_numeros(maps_true,gamma_star))


}
rm(maps_true)

```

And for each voronoi cell, we compute $\hat{P}_{\tilde{n}}(\Gamm^{\star},j, \Ytrue) = \frac{1}{\tilde{n}} \sum^{\tilde{n}}_{k=1} \mathbb{1}_{\yinclust{\Ytrue(\tilde{X}^{(k)})}{\Gamm^{\star}}{j} }\frac{f_{X}(\tilde{X}^{(k)})}{\biais(\tilde{X}_{k})}$ with $\tilde{n} = 10^7$

Here are the probabilities obtained with the true maps

```{r}
get_probas(numeros, unlist(densite_vec))
```

## With the predicted maps

```{r}
X_training = Xtilde[1:1300,]
Y_training = Campbell2D(X_training,z1,z2)

set.seed(1)
fp = Fpca2d.Wavelets(Y_training, wf = "d4", boundary = "periodic", J = 1, ncoeff = 2000, rank = 6)

  
model = km_Fpca2d(formula = ~1, design = data.frame(x = X_training)[,1:7], response = fp, covtype = "matern5_2",control = list(trace = 0))
```

```{r}
registerDoParallel(cores = 10)

batch_size = 10^4 #we will compute the voronoi cell by batch of 10^4 maps

numeros_pred = c()
for(batch in 1:(nrow(Xtilde)%/%batch_size)){ #for each batch
  if(batch %% 50 == 0){print(batch)}
  Xtilde_batch = Xtilde[((batch-1)*batch_size+1):(batch*batch_size),] #we get the inputs of the batch
  map_metamodel = foreach(i = 1:100, .combine = "c") %dopar% {predict.km_Fpca2d(object = model, newdata = data.frame(Xtilde_batch[((i-1)*100+1):(i*100),1:7]), type = "UK", compute = FALSE, checkNames = FALSE)$mean} #we predict the maps associated to these inputs
  map_metamodel = array(map_metamodel, dim = c(64,64,10000)) 

  numeros_pred = c(numeros_pred, get_numeros(map_metamodel,gamma_star)) #computed the associated voronoi cells number

}

numeros_pred[1:1300] = numeros[1:1300] #the training voronoi cell number are affected to the training maps
```

Here are the probabilities obtained with the predicted maps

```{r}
get_probas(numeros_pred, unlist(densite_vec))
```

