---
title: "Quantization error"
output: html_notebook
---

\newcommand{\Ecal}{\mathcal{Y}}
\newcommand{\Esp}[1]{\mathbb{E}\left[#1\right]}
\newcommand{\Espf}[1]{\mathbb{E}_{f_{X}}\left[#1\right]}
\newcommand{\Espbiais}[1]{\mathbb{E}_{\biais}\left[#1\right]}
\newcommand{\centro}{\gamma}
\newcommand{\Gamm}{\Gamma}
\newcommand{\norm}[1]{\lVert #1 \lVert_{\Ecal}}
\newcommand{\rep}{q_{\Gamm}}
\newcommand{\qgs}{q_{{\Gamm}^{\star}}}
\newcommand{\qgk}{q_{{\Gamm}^{[k]}}}
\newcommand{\scalprodE}[2]{\langle #1,#2\rangle_{\Ecal}}
\newcommand{\scalprod}[2]{\Esp{\scalprodE{#1}{#2}}}
\newcommand{\scalprodomega}[2]{\Esp{\scalprodE{#1}{#2}}}
\newcommand{\biais}{\nu}
\newcommand{\repo}{q^{0}_{\Gamm}}
\newcommand{\Xtildek}{\tilde{X}^{k}}
\newcommand{\Espprod}[1]{\mathbb{E}_{\Omega_{1}, \Omega_{2}}\left[#1\right]}
\newcommand{\var}{\mathbb{V}}
\newcommand{\clust}[2]{C^{#1}_{#2}}
\newcommand{\yinclust}[3]{#1 \in \clust{#2}{#3}}
\newcommand{\card}{\ell}
\newcommand{\campbell}{h}
\newcommand{\aff}{a}
\newcommand{\Jcal}{\mathcal{J}}
\newcommand{\Ytrue}{{Y}}
\newcommand{\Ypred}{\hat{Y}}
\newcommand{\Ysimu}{Y_{simu}}
\newcommand{\camprandom}{H}
\newcommand{\dime}{64}
\newcommand{\Gammaref}{\Gamma^{\star}}
\newcommand{\Gammapred}{\hat\Gamma_{\star}}
\newcommand{\Gammasimu}{\Gamma_{simu}}
\newcommand{\erreurproba}{\varepsilon}
\newcommand{\erreurprobarelative}{\delta}
\newcommand{\erreurprobarelativecoastal}{\erreurprobarelative}

\newcommand{\nbgamma}{100}
\newcommand{\nbpilot}{v}
\newcommand{\ntrue}{n_{t}}
\newcommand{\npred}{n_{pred}}
\newcommand{\nsimu}{n_{\mathrm{simu}}}
\newcommand{\Dspace}{\chi}
\newcommand{\supp}{{\mathrm{supp}}}
\newcommand{\thresh}{t}
\newcommand{\estim}{\hat{E}}
\newcommand{\nbsim}{m_{\mathrm{simu}}}
\newcommand{\ntrain}{n_{\mathrm{train}}}
\newcommand{\ntest}{n_{\mathrm{test}}}
\newcommand{\eqdef}{:=}
\newcommand{\Ypca}{Y^{\mathrm{pca}}}
\newcommand{\Yproj}{Y_{\mathrm{proj}}}
\DeclareMathOperator*{\argmax}{arg\,max}
\DeclareMathOperator*{\argmin}{arg\,min}
\newcommand\dsone{\mathds{1}}
\newcommand{\Ecal}{\mathcal{E}}
\newcommand{\Esp}[1]{\mathbb{E}\left[#1\right]}
\newcommand{\centro}{\gamma}
\newcommand{\Gamm}{\Gamma}
\newcommand{\norm}[1]{\lVert #1 \lVert_{\mathcal{E}}}
\newcommand{\rep}{q_{\Gamm}}
\newcommand{\qgs}{q_{{\Gamm}^{\star}}}
\newcommand{\qgk}{q_{{\Gamm}^{[k]}}}
\newcommand{\scalprodE}[2]{\langle #1,#2\rangle_{\mathcal{E}}}
\newcommand{\scalprod}[2]{\Esp{\scalprodE{#1}{#2}}}
\newcommand{\repo}{q^{0}_{\Gamm}}
\newcommand{\Xtildek}{\tilde{X}^{k}}


With the notebooks lloyd_true.Rmd and lloyd_predict.Rmd, we obtained two different sets of prototype maps : $\Gamm^{\star}$ obtained with the maps and $\hat{\Gamm}^{\star}$ with the predicted maps. 

Therefore, to evaluate the quality of the representive maps obtained in the predicted case, we compute the relative error $\frac{\hat{e}(\Gammapred)-\hat{e}(\Gammaref)}{\hat{e}(\Gammaref)}$ with $\hat{e}(\Gamm) = \left(\frac{1}{10^6} \sum_{k = 1}^{10^6} \norm{\Ytrue(\tilde{X}^{(k)}) - \rep(\Ytrue(\tilde{X}^{(k)}))}^2\frac{f_{X}(\tilde{X}^{(k)})}{\biais(\tilde{X}_{k})}\right)^{\frac{1}{2}}$ the empirical quantization error. It evaluates the prototypes maps obtained with the predicted maps compared to the ones obtained with the real maps.

```{r}
load("NewFitting_Charlie_v090821.RData")

source("Campbell2D.R")
source("Campbell_utils.R")
source.all("GpOutput2D-main/GpOutput2D/R")
```

```{r}
dim_map = c(64,64)

z1 = seq(-90,90,l=dim_map[1])
z2 = seq(-90,90,l=dim_map[2])
```

```{r}
set.seed(1234)
n=10^6
Xtilde = matrix(runif(n =5*n), ncol = 5)
Xtilde = cbind(Xtilde, sample(1:10,size = n, replace = TRUE) / 10)

unif = runif(n) 
Xtilde = cbind(Xtilde, (unif <= 8/13)*runif(n))

Xtilde = cbind(Xtilde, rep(-1,n))
Xtilde = transform_X(Xtilde)

```

```{r}
Xtilde_phy = ((Xtilde + 1)/6)[,1:7]
for(i in 1:5){
  Xtilde_phy[,i] = Xtilde_phy[,i] * (df_bornes[i,2]-df_bornes[i,1]) + df_bornes[i,1]
}
Xtilde_phy[,6] = Xtilde_phy[,6]*10

registerDoParallel(cores = 24)

densite_vec = foreach(it = 1:10, .combine = "c") %dopar% {
  densite_ratio_full_vec(Xtilde_phy[((it-1)*10^5 + 1):(it*10^5),])
}
```


We load the obtained representative maps 

```{r}
load("lloyd_true_notebook.RData")
load("lloyd_res_true.RData")
gamma_true = lloyd_res_true$gamma

load("lloyd_res_predict.RData")
gamma_pred = lloyd_res_predict$gamma
```

The function get_distance computes for each map of a database of maps, the distance between the map and its closest prototype map.
```{r}
get_distance = function(maps, gamma){
  return(Vectorize(function(it){distance_gamma(maps[,,it], gamma)$dist})(1:dim(maps)[3]))
}
```

The function sum_quanti_error compute $\sum_{k = 1}^{n} \norm{\Ytrue(\tilde{X}^{(k)}) - \rep(\Ytrue(\tilde{X}^{(k)}))}^2\frac{f_{X}(\tilde{X}^{(k)})}{\biais(\tilde{X}_{k})}$
```{r}
sum_quanti_error = function(maps, gamma, densite_vec){
    distances = get_distance(maps,gamma)
    return(sum(distances^2*densite_vec))
}
```

We compute $\sum_{k = 1}^{10^6} \norm{\Ytrue(\tilde{X}^{(k)}) - \rep(\Ytrue(\tilde{X}^{(k)}))}^2\frac{f_{X}(\tilde{X}^{(k)})}{\biais(\tilde{X}_{k})}$ for $\Gamm = \Gamm^{\star}$ and  $\Gamm = \hat{\Gamm}^{\star}$

```{r, results='hide'}
sum_error_true = 0
sum_error_pred = 0
for(it in 1:10){
    print(it)
    maps = Campbell2D(Xtilde[((it-1)*10^5+1):(it*10^5),], z1, z2)
    sum_error_true = sum_error_true + sum_quanti_error(maps, gamma_true, densite_vec[((it-1)*10^5+1):(it*10^5)])
    sum_error_pred = sum_error_pred + sum_quanti_error(maps, gamma_pred, densite_vec[((it-1)*10^5+1):(it*10^5)])

}

rm(maps)
```
We now compute the relative difference between the quantization error obtained with the predicted maps and with the true maps.

```{r}
abs(sqrt(sum_error_true/10^6) - sqrt(sum_error_pred/10^6))/sqrt(sum_error_pred/10^6)
```








