---
title: "Importance sampling performance metrics"
output: html_notebook
---
\newcommand{\Gamm}{\Gamma}
\newcommand{\scalprod}[2]{\Esp{\scalprodE{#1}{#2}}}
\newcommand{\biais}{\nu}
\newcommand{\var}{\mathbb{V}}
\newcommand{\clust}[2]{C^{#1}_{#2}}
\newcommand{\yinclust}[3]{#1 \in \clust{#2}{#3}}
\newcommand{\Ytrue}{{Y}}
\newcommand{\ntrue}{n_{\mathrm{maps}}}
\newcommand{\estim}{\hat{E}}
\newcommand{\nvar}{n_{v}}

The effect of the importance sampling (IS) on the quantization is assessed, for a given Voronoi cell $\clust{\Gamm}{j}$, through two metrics:

- The IS coefficient of variation of the membership probability, $\epsilon_P^{IS}(\tilde{n},\Gamm^{r},j)$, which is an estimator of $\frac{\sqrt{\var\left(\hat{P}_{\tilde{n}}(\Gamm,j, \Ytrue)\right)}}{\hat{P}_{\tilde{n}}(\Gamm,j, \Ytrue)}$. It measures an
 error due to the importance sampling in the estimation of the probability
of the Voronoi cell n°$j$.
- The IS centroid standard deviation, $\epsilon_{\Gamm}^{IS}(\ntrue,\Gamm^{r},j)$,
which is related to the variance $\var\left(\estim_{\ntrue}(\Gamm,j,\Ytrue)\right)$. It characterizes the error coming from importance sampling in the estimation of the centroid of the Voronoi cell n°$j$. 
More precisely, $\estim_{\ntrue}(\Gamm,j,\Ytrue)$ is a vector of the size of the maps, and we investigate the diagonal terms $(v_{i})_{i=1}^{64^2} = \var\left((\estim_{\ntrue}(\Gamm,j,\Ytrue))_{i}\right)$ of the covariance matrix.  
Finally, the $90\%$-quantile of these $64^2$ variances is computed, and its square root gives the metric $\epsilon_{\Gamm}^{IS}(\ntrue,\Gamm^{r},j)$. 



# IS coefficient of variation of the membership probability

Considering $(\tilde{X}^{k})_{k=1}^{\nvar}$ a large number of i.i.d random variable of density $\nu$, an empirical estimator of $\var\left(\mathbb{1}_{\yinclust{\Ytrue(\tilde{X})}{\Gamm}{j}}\frac{f_{X}(\tilde{X})}{\biais(\tilde{X})}\right)$ is,
$$\frac{1}{\nvar -1}\sum_{k=1}^{\nvar}\left[\mathbb{1}_{\yinclust{\Ytrue(\tilde{X}^{k})}{\Gamm}{j}}\frac{f_{X}(\tilde{X}^{k})}{\biais(\tilde{X}^{k})} - \hat{P}_{\nvar}(\Gamm,j,\Ytrue)\right]^2~.$$

Then an estimator of $\frac{\sqrt{\var\left(\hat{P}_{\tilde{n}}(\Gamm,j, \Ytrue)\right)}}{\hat{P}_{\tilde{n}}(\Gamm,j, \Ytrue)}$ is the IS relative standard deviation
$$\epsilon_P^{IS}(\tilde{n},\Gamm^{r},j) = \frac{1}{\sqrt{\tilde{n}}}\frac{\sqrt{\frac{1}{\nvar -1}\sum_{k=1}^{\nvar}\left[\mathbb{1}_{\yinclust{\Ytrue(\tilde{X}^{k})}{\Gamm}{j}}\frac{f_{X}(\tilde{X}^{k})}{\biais(\tilde{X}^{k})} - \hat{P}_{\nvar}(\Gamm,j,\Ytrue)\right]^2}}{\hat{P}_{\nvar}(\Gamm,j,\Ytrue)}~.$$ 
We work here with $\nvar = 10^5$ and $\tilde{n} = 10^7$.


```{r}
source.all("GpOutput2D-main")
source.all("FunQuant-0.1.3/R")
source("Campbell2D.R")
source("Campbell_utils.R")
```

```{r}
dim_map = c(64,64)

z1 = seq(-90,90,l=dim_map[1])
z2 = seq(-90,90,l=dim_map[2])
```

We sample $(\tilde{x}^k)_{k \in \{1,\dots,10^5\}}$ i.i.d of density function $\biais$

```{r}
set.seed(1234)
n=10^5
Xtilde = matrix(runif(n =5*n), ncol = 5)
Xtilde = cbind(Xtilde, sample(1:10,size = n, replace = TRUE) / 10) 

unif = runif(n) 
Xtilde = cbind(Xtilde, (unif <= 8/13)*runif(n))

Xtilde = cbind(Xtilde, rep(-1,n))
Xtilde = transform_X(Xtilde)

```


We compute $\left(\frac{f_{X}(\tilde{x}^k)}{\biais(\tilde{x}^k)}\right){_{k \in \{1,\dots,10^5\}}}$ 

```{r}
Xtilde_phy = ((Xtilde + 1)/6)[,1:7]
for(i in 1:5){
  Xtilde_phy[,i] = Xtilde_phy[,i] * (df_bornes[i,2]-df_bornes[i,1]) + df_bornes[i,1]
}
Xtilde_phy[,6] = Xtilde_phy[,6]*10

registerDoParallel(cores = 24)

density_ratio = compute_density_ratio(fX,g,Xtilde_phy)
```

We sample $(\Gamma_{r})_{r \in \{1,\dots, n_{\Gamm}\}}$

```{r}
load("lloyd_res_true.RData")
gamma_star = lloyd_res_true$gamma #the prototype maps obtained with the true maps

set.seed(2)
gamma_it_list = list()
for(it in 1:100){
  gamma_it_list[[it]] = lapply(1:5, function(i){gamma_star[[i]]*matrix(runif(64^2,0.8,1.2), ncol = 64, nrow = 64)})
}
```


Compute $Y(\tilde{x}^k)_{k \in \{1,\dots,10^5\}}$ the sample of real maps

```{r}
maps_true = Campbell2D(Xtilde,z1,z2)

```

Associate each of these $10^5$ maps to their voronoi cell for each $\Gamm^{r}$



```{r}
#load("perf_probas.RData")
```

Computation of $\var\left(\hat{P}_{\tilde{n}}^{\mathrm{true}}(\Gamm,j)\right)$ $\forall \Gamm \in (\Gamm^{r})_{r\in\{1,\dots,100\}}$ and $\forall j \in \{1,\dots,5\}$ with $\tilde{n} = 10^7$



```{r}
list_for_std = list()
std_list = std_proba(outputs = maps_true, gamma_list = gamma_it_list, density_ratio = density_ratio, cells = 1:5, nv = 10^7)

relative_std = unlist(std_list)

```

We plot the distribution of the errors

```{r, fig.height = 5, fig.width = 5}
boxplot(relative_std, col = "darkolivegreen2", ylab = "Proba. relative standard error", cex.lab=1.3, cex.axis = 1.3) 

```
## IS centroid standard deviation


We have 
$(\estim_{\ntrue}(\Gamm,j,\Ytrue))_{i} = \frac{\frac{1}{\ntrue} \sum^{\ntrue}_{k=1} \Ytrue_{,i}(\tilde{X}^{k})\mathbb{1}_{\yinclust{\Ytrue(\tilde{X}^{k})}{\Gamm}{j} }\frac{f_{X}(\tilde{X}^{k})}{\biais(\tilde{X}^{k})}}{\hat{P}_{\ntrue}(\Gamm,j,\Ytrue)}$ 
with $\Ytrue_{,i}(\tilde{X}^{k})$ the $i$th pixel of the map $\Ytrue(\tilde{X}^{k})$.

As detailed in \cite{Kempen}, the variance of the ratio of two random variables $A$ and $B$ can be approximated by the following expression:
$$\var\left(\frac{A}{B}\right) \approx \frac{\mu_{A}^{2}}{\mu_{B}^2}\left[\frac{\var(A)}{\mu_{A}^2}-2\frac{cov(A,B)}{\mu_A\mu_{B}} + \frac{\var(B)}{\mu_B^2}\right]~.$$ with $\mu_A,\mu_{B}$ the mean of $A$ and $B$.

In our case,  we denote $A_{i} = \frac{1}{\ntrue} \sum^{\ntrue}_{k=1} \Ytrue_{,i}(\tilde{X}^{k})\mathbb{1}_{\yinclust{\Ytrue(\tilde{X}^{k})}{\Gamm}{j} }\frac{f_{X}(\tilde{X}^{k})}{\biais(\tilde{X}^{k})}$ for $i \in \{1,\dots,64^2\}$,
and $B = \hat{P}_{\ntrue}(\Gamm,j,\Ytrue)$


Then, with a large sample $(\tilde{X}^{k})_{k=1}^{\nvar}$ of $\tilde{X}$, we can compute the empirical estimation of the needed quantities:

- $\hat\mu_{A_{i}} = \frac{1}{\nvar} \sum^{\nvar}_{k=1} \Ytrue_{,i}(\tilde{X}^{k})\mathbb{1}_{\yinclust{\Ytrue(\tilde{X}^{k})}{\Gamm}{j} }\frac{f_{X}(\tilde{X}^{k})}{\biais(\tilde{X}^{k})}$
- $\hat{\var}(A_{i}) = \frac{1}{\ntrue} \frac{1}{\nvar-1} \sum^{\nvar}_{k=1} \left(\Ytrue_{,i}(\tilde{X}^{k})\mathbb{1}_{\yinclust{\Ytrue(\tilde{X}^{k})}{\Gamm}{j} }\frac{f_{X}(\tilde{X}^{k})}{\biais(\tilde{X}^{k})} - \hat\mu_{A_{i}}\right)^2$
- $\hat\mu_{B} = \hat{P}_{\nvar}(\Gamm,j,\Ytrue) =  \frac{1}{\nvar} \sum^{\nvar}_{k=1} \mathbb{1}_{\yinclust{\Ytrue(\tilde{X}^{k})}{\Gamm}{j} }\frac{f_{X}(\tilde{X}^{k})}{\biais(\tilde{X}^{k})}$ 
- $\hat{\var}(B) = \frac{1}{\ntrue} \frac{1}{\nvar-1} \sum^{\nvar}_{k=1} \left(\mathbb{1}_{\yinclust{\Ytrue(\tilde{X}^{k})}{\Gamm}{j} }\frac{f_{X}(\tilde{X}^{k})}{\biais(\tilde{X}^{k})} - \hat\mu_{B}\right)^2$
- $\hat{cov}(A_{i},B) = \frac{1}{\ntrue} \frac{1}{\nvar-1}\sum^{\nvar}_{k=1}\left(\Ytrue_{,i}(\tilde{X}^{k})\mathbb{1}_{\yinclust{\Ytrue(\tilde{X}^{k})}{\Gamm}{j} }\frac{f_{X}(\tilde{X}^{k})}{\biais(\tilde{X}^{k})} - \hat\mu_{A_{i}}\right)\left(\mathbb{1}_{\yinclust{\Ytrue(\tilde{X}^{k})}{\Gamm}{j} }\frac{f_{X}(\tilde{X}^{k})}{\biais(\tilde{X}^{k})} - \hat\mu_{B}\right)$

Then,  $\forall i \in \{1\dots64^2\}$, i.e. for each pixel, the standard deviation can be computed : 
$$\hat{e}((\estim_{\ntrue}(\Gamm,j,\Ytrue))_{i}) = \sqrt{\hat{\var}\left((\estim_{\ntrue}(\Gamm,j,\Ytrue))_{i}\right)}.$$

Finally, the $90\%$-quantile over $i$ is computed for a given Voronoi cell $\clust{\Gamm}{j}$ to compute the IS standard deviation $\epsilon_{\Gamm}^{IS}(\ntrue,\Gamm,j)$, with $\ntrue = 10^6$ and $\nvar = 10^5$.





First, computation of $\var\left(\frac{A_{i}}{B}\right) \approx \frac{\mu_{A_{i}}^{2}}{\mu_{B}^2}\left[\frac{\var(A_{i})}{\mu_{A_{i}}}-2\frac{cov(A_{i},B)}{\mu_{A_{i}}\mu_{B}} + \frac{\var(B)^2}{\mu_B^2}\right]$ with $\mu_A,\mu_{B}$ $\forall i \in \{1,\dots,64^2\}$ and $\forall j \in \{1,\dots,5\}, \forall \Gamm \in (\Gamm^{r})$

with $A_{i} = \frac{1}{\ntrue} \sum^{\ntrue}_{k=1} \Ytrue_{,i}(\tilde{X}^{k})\mathbb{1}_{\yinclust{\Ytrue(\tilde{X}^{k})}{\Gamm}{j} }\frac{f_{X}(\tilde{X}^{k})}{\biais(\tilde{X}^{k})}$ for $i \in \{1,\dots,64^2\}$,
and $B = \hat{P}_{\ntrue}(\Gamm,j,\Ytrue)$

```{r}
std_ratio_list = std_centroid(outputs = maps_true, gamma_list = gamma_it_list, density_ratio = density_ratio, cells = 1:5, nv = 10^6)

```

Then : Computational of the $90\%$-quantile over i of $\var\left(\frac{A_{i}}{B}\right)$
```{r}
quantile_std_ratio = lapply(1:5, function(i){std_ratio_list[[i]]})
for(it in 1:5){for(j in 1:5){quantile_std_ratio[[it]][[j]] = quantile(quantile_std_ratio[[it]][[j]], 0.9)}}

quantile_std_ratio = unlist(quantile_std_ratio)
```

We plot the distribution $\forall \Gamm \in (\Gamm^{r})_{r\in\{1,\dots,100\}}$ and $\forall j \in \{1,\dots,5\}$

```{r, fig.height = 5, fig.width = 5}
boxplot(quantile_std_ratio, col = "darkolivegreen2", ylab = "Centroid standard error",cex.lab=1.3, cex.axis = 1.3)
```






