---
title: "Prototype Maps Algorithm with predicted maps"
output: html_notebook
---

\newcommand{\Gamm}{\Gamma}
\newcommand{\biais}{\nu}

Here we will perform the Prototype Maps Algorithm exactly as in the PMalgo_true.Rmd notebook, but with predicted maps instead of the true campbell maps.

We use the hyperparameters tuned in the notebook perf_probas.Rmd with the cross validation : $\tilde{K} = 2000$ and $n_{pc} = 6$



```{r}
source.all("GpOutput2D-main")
source.all("FunQuant-0.1.3/R")
source("Campbell2D.R")
source("Campbell_utils.R")
```


```{r}
dim_map = c(64,64)

z1 = seq(-90,90,l=dim_map[1])
z2 = seq(-90,90,l=dim_map[2])

```

We sample $(tilde{x}^k)_{k \in \{1,\dots,10^6\}}$ i.i.d of density function $\biais = \biais_{1}\times\dots\times \biais_{7}$ with $\forall i \in \{1,\dots,5\}, \biais_{i} = \mathbb{1}_{[0,1]}$, $\biais_{6} = \frac{1}{10}\sum_{k=1}^{10}\delta_{\frac{1}{10}}$ and $\biais_{7} = \frac{5}{13}  \delta_{0} + (\frac{8}{13})\mathbb{1}_{]0,1]}$.

Then we perform a linear transformation of $(tilde{x}^k)_{k \in \{1,\dots,10^6\}}$ so that $tilde{x}^k \in [-1,5]^7$.

We also compute $(tilde{x}_{phy}^k)_{k \in \{1,\dots,10^6\}}$ that is a linear transformation of $tilde{x}$ in the support of $f_{X}$, so that we compute the weights $\left(\frac{f_{X}(tilde{x}^k)}{\biais(tilde{x}^k)}\right){_{k \in \{1,\dots,10^6\}}}$.

```{r}
set.seed(1234)
n=10^6
Xtilde = matrix(runif(n =5*n), ncol = 5)
Xtilde = cbind(Xtilde, sample(1:10,size = n, replace = TRUE) / 10)

unif = runif(n) 
Xtilde = cbind(Xtilde, (unif <= 8/13)*runif(n))

Xtilde = cbind(Xtilde, rep(-1,n))
Xtilde = transform_X(Xtilde)
X_training = Xtilde[1:1300,]
X_test = Xtilde[1301:n,]
Y_training = Campbell2D(X_training,z1,z2)
```



```{r}
Xtilde_phy = ((Xtilde + 1)/6)[,1:7]
for(i in 1:5){
  Xtilde_phy[,i] = Xtilde_phy[,i] * (df_bornes[i,2]-df_bornes[i,1]) + df_bornes[i,1]
}
Xtilde_phy[,6] = Xtilde_phy[,6]*10


registerDoParallel(cores = 24)

density_ratio = foreach(batch = 1:20)%do%{
  print(batch)
  compute_density_ratio(fX, g, Xtilde_phy[((batch-1)*5*10^4+1):(batch*5*10^4),])}

  
```


```{r}

set.seed(1)

metamodel = fit_metamodel(design_train = data.frame(x = X_training)[,1:7], outputs_train = Y_training, seed = 1, ncoeff = 2000, npc = 6,control = list(trace = 0))



```

maps_metamodel is a list of 10 elements : each element is a batch of $10^5$ maps

```{r}
set.seed(1)

maps_metamodel = lapply(1:20, function(it){predict_outputs(metamodel_fitted = metamodel, design_test = data.frame(Xtilde[((it-1)*5*10^4+1):(it*5*10^4),1:7]))}) #predict the  

maps_metamodel[[1]][,,1:1300] = Y_training

```

We take the same $\Gamm_{0}$ as the one used in the lloyd_true.Rmd notebook, as the objective here is to compare the method with the true maps to the method with the predicted maps.

```{r}
load("gamma_0.RData")
```

## Prototype Maps Algorithm


```{r,  results='hide'}
lloyd_res_predict = proto_map_algo(gamma = gamma, outputs = maps_metamodel, density_ratio = density_ratio, batch = TRUE, print_progress = TRUE)
```

```{r}

for(i in 1:5){print(plot_map(lloyd_res_predict$gamma[[i]]))}
```
```{r}
save(lloyd_res_predict, file = "lloyd_res_predict.RData")
```


```{r}
rm(maps_metamodel)
save.image("PM_algo_pred.RData")

```

