---
title: "Prototype Maps Algorithm with true maps"
output: html_notebook
---


\newcommand{\Gamm}{\Gamma}
\newcommand{\biais}{\nu}
\newcommand{\campbell}{h}


This notebook performs the Prototype Maps Algorithm in the Campbell2D case with the true Campbell maps.

## Introduction 

```{r}
source.all("GpOutput2D-main")
source.all("FunQuant-0.1.3/R")
source("Campbell2D.R")
source("Campbell_utils.R")
```
The performance of the method is evaluated on an analytical test case, called the Campbell2D function. This function has eight inputs (d=8) and a spatial map as output, i.e a function which depends on two inputs $(\textbf{z} = (z_{1},z_{2}))$ corresponding to spatial coordinates. 

\begin{align*}
\campbell\colon \;\;\;\;\;\;\;\;\;\; [-1,5]^{8} &\longrightarrow \mathbb{L}^{2}([-90,90]^{2}) \\
\textbf{x} = (x_{1},\dots, x_{8}) &\longmapsto \campbell_{\textbf{x}}(\textbf{z}).
\end{align*}
where $\textbf{z} = (z_{1}, z_{2}) \in [-90,90]^{2}$, $x_{j} \in [-1,5]$ for $j = 1,\dots,8$ and 
\begin{align*}
\campbell_{\textbf{x}}(z_{1}, z_{2}) &=    x_{1}\exp[-\frac{(0.8z_{1}+0.2z_{2}-10x_{2})^2}{60x_{1}^2}] \\
&+  (x_{2}+x_{4})\exp[\frac{(0.5z_1+0.5z_2)x_{1}}{500}] +  x_{5}(x_{3}-2)\exp[-\frac{(0.4z_{1}+0.6z_{2}-20x_{6})^2}{40x_{5}^2}] \\
&+ 
(x_{6}+x_{8})\exp[\frac{(0.3z_1+0.7z_2)x_{7}}{250}]
\end{align*}

As in the coastal case we work in 7 dimensions, we fix don't consider the 8th dimension of the input : we set $x_{8} = -1$

We will work with Campbell maps 64x64.

```{r}
dim_map = c(64,64)

z1 = seq(-90,90,l=dim_map[1])
z2 = seq(-90,90,l=dim_map[2])

```

We sample $(\tilde{X}^{(k)})_{k \in \{1,\dots,10^6\}}$ i.i.d of density function $\biais = \biais_{1}\times\dots\times \biais_{7}$ with $\forall i \in \{1,\dots,5\}, \biais_{i} = \mathbb{1}_{[0,1]}$, $\biais_{6} = \frac{1}{10}\sum_{k=1}^{10}\delta_{\frac{1}{10}}$ and $\biais_{7} = \frac{5}{13}  \delta_{0} + (\frac{8}{13})\mathbb{1}_{]0,1]}$.

Then we perform a linear transformation of $(\tilde{X}^{(k)})_{k \in \{1,\dots,10^6\}}$ so that $\tilde{X}^{(k)} \in [-1,5]^7$.

We also compute $(\tilde{X}_{phy}^{(k)})_{k \in \{1,\dots,10^6\}}$ that is a linear transformation of $\tilde{X}$ in the support of $f_{X}$, so that we compute the weights $\left(\frac{f_{X}(\tilde{X}^{(k)})}{\biais(\tilde{X}^{(k)})}\right){_{k \in \{1,\dots,10^6\}}}$.


```{r}
set.seed(1234)
n=10^6
Xtilde = matrix(runif(n =5*n), ncol = 5)
Xtilde = cbind(Xtilde, sample(1:10,size = n, replace = TRUE) / 10)

unif = runif(n) 
Xtilde = cbind(Xtilde, (unif <= 8/13)*runif(n))

Xtilde = cbind(Xtilde, rep(-1,n))
Xtilde = transform_X(Xtilde)

```


```{r}
Xtilde_phy = ((Xtilde + 1)/6)[,1:7]
for(i in 1:5){
  Xtilde_phy[,i] = Xtilde_phy[,i] * (df_bornes[i,2]-df_bornes[i,1]) + df_bornes[i,1]
}
Xtilde_phy[,6] = Xtilde_phy[,6]*10

registerDoParallel(cores = 24)

density_ratio = foreach(batch = 1:20)%do%{
  print(batch)
  compute_density_ratio(fX, g, Xtilde_phy[((batch-1)*5*10^4+1):(batch*5*10^4),])}

  


```
```{r}
save.image("PMalgo_true.RData")
```


## Database of the $10^6$ real maps

maps_true is a list of 10 elements : each element is a batch of $10^5$ maps
```{r}

maps_true = lapply(1:20, function(it){
    print(it)
    Campbell2D(Xtilde[((it-1)*5*10^4+1):(it*5*10^4),], z1, z2)})



```

We sample randomly $\Gamm_{0}$

```{r}

set.seed(709000)
indices = sample(1:(5*10^4), 5)

gamma = lapply(1:5, function(j){maps_true[[1]][,,indices[j]]})

save(gamma, file = "gamma_0.RData")
```

## Prototype Maps Algorithm algorithm


```{r, results='hide'}
lloyd_res_true = proto_map_algo(gamma = gamma, outputs = maps_true, density_ratio = density_ratio, batch = TRUE, print_progress = TRUE)


```
```{r}
ee = estim_num_centroid(outputs = maps_true, cell_numbers = cccc, density_ratio = density_ratio, cell = 1, batch = TRUE)

ee2 = estim_num_centroid(outputs = abind(maps_true[[1]], maps_true[[2]], along = 3), cell_numbers = unlist(cccc), density_ratio = unlist(density_ratio), cell = 1, batch = FALSE)
```


Visualisation of the obtained prototype maps.

```{r}
for(i in 1:5){print(plot_map(lloyd_res_true$gamma[[i]], min = min(unlist(lloyd_res_true$gamma)), max = max(unlist(lloyd_res_true$gamma))))}
```

```{r}
rm(maps_true)
save.image("PMalgo_true.RData")
save(lloyd_res_true, file = "lloyd_res_true.RData")
```
