---
title: "long_example"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{long_example}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width=8, 
  fig.height=6
)
```

```{r setup}
library(FunQuant)

library(randtoolbox)
library(ggplot2)
library(evd)
library(gridExtra)
```

```{r}
set.seed(14)
```

We define the spatial function we investigate here, taking as inputs a vector in $\mathbb{R}^2$, and returning a map 20x20.

```{r}
func2D <- function(X){
  Zgrid <- expand.grid(z1 = seq(-5,5,l=20),z2 = seq(-5,5,l=20))
  n<-nrow(X)
  Y <- lapply(1:n, function(i){(X[i,2] > -0.1)*X[i,2]*X[i,1]*exp(-((0.8*Zgrid$z1+0.2*Zgrid$z2-10*X[i,1])**2)/(60*X[i,1]**2))*(Zgrid$z1-Zgrid$z2)*cos(X[i,1]*4)^2*sin(X[i,2]*4)^2})
  Ymaps<- array(unlist(Y),dim=c(20,20,n))
  return(abs(Ymaps))
}
```

We create a function to plot the spatial outputs 

```{r}
plot_map = function(map, max = NULL, min = NULL){
  gamma_toplot = expand.grid(seq(-5,5,l=20),seq(-5,5,l=20))
  gamma_toplot$f = as.numeric(map)
  if(is.null(max))
  {p = ggplot(gamma_toplot) + geom_raster(aes(x = Var1, y = Var2, fill = f)) + scale_fill_continuous(type = "viridis",direction = -1, name = "h") + theme_bw()}
  else{p = ggplot(gamma_toplot) + geom_raster(aes(x = Var1, y = Var2, fill = f)) + scale_fill_continuous(type = "viridis", direction = -1, limits = c(min, max), name = "h") + theme_bw()  + theme(legend.text = element_text(size=13),legend.title = element_text(size=13))}
  return(p)
}
```


We define the density function of the random variable X. Its support is $[-1,1]^2$

```{r}
f2 = function(x){
  res = 0
  ptrunc = pgev(-1, loc=-0.4,scale=0.1) + 1 - pgev(1, loc=-0.4,scale=0.1)
  if(x>=-1 & x < 1){res = dgev(x, loc=-0.4,scale=0.1)/(1-ptrunc)}
  return(res)
}
f1 = function(x){
  if(x > -1 & x < 1){return(1/2)}
  else{return(0)}
}
fX = function(x){f1(x[1])*f2(x[2])}
```

We define the importance sampling density function

```{r}
g = function(x){
  if(sum(x > -1) == length(x) & sum(x < 1) == length(x)){return(1/4)}
  else{return(0)}
}
```

We introduce the design of experiments

```{r}
design = as.data.frame(halton(400,2))*2-1
outputs = func2D(design)
```

We plot example of the maps

```{r}

plot_list_examples = list(plot_map(outputs[,,2]), plot_map(outputs[,,241]))

do.call("grid.arrange", c(plot_list_examples, ncol=2))
```
We can note that 182 of the 400 outputs are maps with only 0 values

```{r}
sum(Vectorize(function(i){abs(sum(outputs[,,i]))})(1:dim(outputs)[3]) == 0)
```
We compute the importance sampling weights
```{r}
density_ratio = compute_density_ratio(f = fX, g = g, inputs = design)

```

We choose the euclidean distance
```{r}
distance_func = function(A1,A2){return(sqrt(sum((A1-A2)^2)))}
```

We perform the quantization without metamodel, only with the 400 computed maps 

```{r}
sum_depth = Vectorize(function(i){sum(outputs[,,i])})(1:dim(outputs)[3])
gamma = lapply(1:5, function(i){outputs[,,which.min(abs(as.numeric(quantile(sum_depth,c(0,0.6,0.7,0.8,0.9))[i]) - sum_depth))[1]]}) #gamma will be the starting set of prototypes of the quantization. We choose an maps of only 0, and the maps with increasing sum of pixels

res_proto = proto_map_algo(gamma = gamma, outputs = outputs, density_ratio = density_ratio, distance_func = distance_func) 
gamma_star_apriori = res_proto$gamma #This is the optimal set of prototype maps obtained with the 400 maps without metamodel

```

Now we tune the hyperparameters of the metamodel.
Our metamodel will be made of a classifier indicating whether a map is full of 0 or not first, and then Functional Principal Components Analysis combined with kriging to predict the maps that are not classified as full of 0. 

We start by tuning the parameters npc and ncoeff of the FPCA, focusing only on the maps that are not full of 0.

We use the function rmse_f_fold that computes, for each pair of tested hyperparameters, a map indicating at each pixel the Root Mean Square error between the values predicted by k-fold cross validation and the real values. 

```{r}
npc_vec = 2:5
ncoeff_vec = c(100,200,300,400)
list_rmse_k_fold = rmse_k_fold(outputs = outputs[,, sum_depth > 0], design = design[sum_depth > 0,], nb_folds = 10, npc_vec = npc_vec, ncoeff_vec = ncoeff_vec, seed = 10, control = list(trace = FALSE)) 
quantile_90 = sapply(list_rmse_k_fold$outputs_rmse, function(x){quantile(x, 0.9)}) #We take the quantile 90% of the rmse maps

best_params = list_rmse_k_fold$grid_cv[quantile_90 == min(quantile_90),] #We identify the pairs of parameters minimizing the quantile 90%

best_params

plot_map(list_rmse_k_fold$outputs_rmse[[2]])
```

We can also tune the hyperparameters regarding the relative error made when computing the Voronoï cells membership probabilities (for a given set of prototypes gamma) with the predicted maps instead of the true maps. We use the function probas_k_fold to this end.

```{r}
list_probas_k_fold = probas_k_fold(outputs = outputs[,, sum_depth > 0], design = design[sum_depth > 0,], nb_folds = 10, density_ratio = density_ratio[sum_depth >0], gamma = gamma_star_apriori, distance_func = distance_func, npc_vec = npc_vec, ncoeff_vec = ncoeff_vec, seed = 10, control = list(trace = FALSE))

```

Once we have the hyperparameters of the FPCA, we can tune the hyperparameters of the random forests classifier. 

Here we choose to tune the hyperparameters "nodesize" and "classwt", and we use the function rf_rmse_k_fold that does the same as rmse_k_fold but by integrating the random forest in the metamodel scheme, and focuses on the classifier hyperparemeters. Thus this function considers all the maps, even the ones full of 0.

```{r}
df_search = expand.grid(classwt1 = seq(0.2,0.8,0.3), nodesize = c(1,3,5))
list_search = list("nodesize" = as.list(df_search[,2]), "classwt" = lapply(1:nrow(df_search), function(i){c(df_search[i,1], 1-df_search[i,1])}))
list_rf_rmse_k_fold = rf_rmse_k_fold(design = design,outputs = outputs, threshold_classification = 0, list_search = list_search, nb_folds = 10, ncoeff = 200, npc = 2, control = list(trace = FALSE), seed = 10)
quantile_90_rf = sapply(list_rf_rmse_k_fold$outputs_rmse, function(x){quantile(x, 0.9)})

best_params_rf = df_search[quantile_90_rf == min(quantile_90_rf),]
best_params_rf

plot_map(list_rf_rmse_k_fold$outputs_rmse[[1]])
```

Likewise, rf_probas_k_fold does the same as probas_k_fold but integrates the random forests classifier, focusing on the classifier hyperparameters.

```{r}
list_rf_probas_k_fold = rf_probas_k_fold(design = design,outputs = outputs, density_ratio = density_ratio, gamma = gamma_star_apriori, distance_func = distance_func,threshold_classification = 0, list_search = list_search, nb_folds = 10, ncoeff = 200, npc = 2, control = list(trace = FALSE), seed = 10)

```

Once we have the hyperparameters for both the FPCA and the classifier, we can predict maps at new inputs.

```{r}
#We generate a sample of inputs with density g
design_test = as.data.frame(matrix(runif(2*10^4), ncol=2)*2-1)
#We compute the true outputs
outputs_test = func2D(design_test)
#We predict the outputs
outputs_pred = predict_outputs(design_train = design, design_test = design_test, outputs_train = outputs, seed = 10, ncoeff = 200, npc = 2, control = list(trace = FALSE), classification = TRUE, control_classification = list("nodesize" = 1, classwt = c(0.5,0.5)), threshold_classification = 0)
#We compute the importance sampling weights
density_ratio_pred = compute_density_ratio(fX,g,design_test)

```

And we can perform the quantization on our $10^4$ predicted maps.

```{r}

# We perform quantization
res_proto_pred = proto_map_algo(gamma = gamma_star_apriori, outputs = outputs_pred, density_ratio = density_ratio_pred, distance_func = distance_func, trace = FALSE)

```
We plot the obtained prototype maps

```{r}
list_plots_pred = list()
for(i in 1:length(res_proto_pred$gamma)){
  list_plots_pred[[i]] = plot_map(res_proto_pred$gamma[[i]])
}
do.call("grid.arrange", c(list_plots_pred, ncol=2))
```


We estimate the relative standard deviation of the membership probabilities of the obtained optimal Voronoi cells.

```{r}
res_std_probas = std_proba(outputs_pred, gamma_list = list(res_proto_pred$gamma), density_ratio = density_ratio_pred, distance_func = distance_func, cells = 1:5, nv = 10^4)

res_std_probas
```

We also estimate the standard deviation of the estimation of each optimal prototype pixel

```{r}
res_std_centroid = std_centroid(outputs = outputs_pred, gamma_list = list(res_proto_pred$gamma), density_ratio = density_ratio_pred, distance_func = distance_func, cells = 1:5, nv = 10^4)

#Then we compute the quantile 90% of each of these standard deviation maps
quantiles_90_std = sapply(res_std_centroid[[1]], function(x){quantile(x, 0.9)})

list_plots_std = list()
for(i in 1:length(res_proto_pred$gamma)){
  list_plots_std[[i]] = plot_map(res_std_centroid[[1]][[i]])
}
do.call("grid.arrange", c(list_plots_std, ncol=2))


```

We now confirm the precision of the metamodel by comparing the probabilities obtained with the true maps and the predicted maps for the optimal prototypes

```{r}
probas_true = get_probas(density_ratio = density_ratio_pred, gamma = res_proto_pred$gamma, outputs = outputs_test, distance_func = distance_func)
probas_pred = res_proto_pred$probas

probas_true
probas_pred
```

We also check that the quantization error obtained with the predicted maps is close to the one obtained with the true maps

```{r}
res_proto_test = proto_map_algo(gamma = gamma_star_apriori, outputs = outputs_test, density_ratio = density_ratio_pred, distance_func = distance_func, trace = FALSE)
quanti_error_test = quanti_error(outputs = outputs_test, gamma = res_proto_test$gamma, density_ratio = density_ratio_pred, distance_func = distance_func)
quanti_error_pred = quanti_error(outputs = outputs_test, gamma = res_proto_pred$gamma, density_ratio = density_ratio_pred, distance_func = distance_func)

quanti_error_pred
quanti_error_test
```

